---
title: "Test"
output: html_document
---

## Loading packages

```{r}
library(tidyverse)
library(lubridate)
library(zoo)
library(boot)
library(rpart)
library(rpart.plot)
library(modelr)
```


## Importing Kaggle data

# Importing Kaggle's Energy generation, demand, and prices data

```{r}
kaggle_energy <- read_csv('data/Energy_demand_Generation_and_Prices_Spain/energy_dataset.csv')

names(kaggle_energy) <- gsub(" ", "_", names(kaggle_energy))
names(kaggle_energy) <- gsub("/", "_", names(kaggle_energy))
names(kaggle_energy) <- gsub("-", "_", names(kaggle_energy))

kaggle_energy
```

# Importing Kaggle's Weather data

```{r}
kaggle_weather <- read_csv('data/Energy_demand_Generation_and_Prices_Spain/weather_features.csv')
kaggle_weather
```

# Pre-processing Kaggle's Weather data: adding variables (columns) of all cities

```{r}
kaggle_weather_Barcelona <- filter(kaggle_weather, city_name == "Barcelona") %>% 
  select(-city_name) %>% 
  rename(temp_Barcelona = temp, 
         temp_min_Barcelona = temp_min, 
         temp_max_Barcelona = temp_max, 
         pressure_Barcelona = pressure, 
         humidity_Barcelona = humidity, 
         wind_speed_Barcelona = wind_speed, 
         wind_deg_Barcelona = wind_deg, 
         rain_1h_Barcelona = rain_1h, 
         rain_3h_Barcelona = rain_3h, 
         snow_3h_Barcelona = snow_3h, 
         clouds_all_Barcelona = clouds_all, 
         weather_id_Barcelona = weather_id, 
         weather_main_Barcelona = weather_main, 
         weather_description_Barcelona = weather_description, 
         weather_icon_Barcelona = weather_icon)

kaggle_weather_Bilbao <- filter(kaggle_weather, city_name == "Bilbao") %>% 
  select(-city_name) %>% 
  rename(temp_Bilbao = temp, 
         temp_min_Bilbao = temp_min, 
         temp_max_Bilbao = temp_max, 
         pressure_Bilbao = pressure, 
         humidity_Bilbao = humidity, 
         wind_speed_Bilbao = wind_speed, 
         wind_deg_Bilbao = wind_deg, 
         rain_1h_Bilbao = rain_1h, 
         rain_3h_Bilbao = rain_3h, 
         snow_3h_Bilbao = snow_3h, 
         clouds_all_Bilbao = clouds_all, 
         weather_id_Bilbao = weather_id, 
         weather_main_Bilbao = weather_main, 
         weather_description_Bilbao = weather_description, 
         weather_icon_Bilbao = weather_icon)

kaggle_weather_Madrid <- filter(kaggle_weather, city_name == "Madrid") %>% 
  select(-city_name) %>% 
  rename(temp_Madrid = temp, 
         temp_min_Madrid = temp_min, 
         temp_max_Madrid = temp_max, 
         pressure_Madrid = pressure, 
         humidity_Madrid = humidity, 
         wind_speed_Madrid = wind_speed, 
         wind_deg_Madrid = wind_deg, 
         rain_1h_Madrid = rain_1h, 
         rain_3h_Madrid = rain_3h, 
         snow_3h_Madrid = snow_3h, 
         clouds_all_Madrid = clouds_all, 
         weather_id_Madrid = weather_id, 
         weather_main_Madrid = weather_main, 
         weather_description_Madrid = weather_description, 
         weather_icon_Madrid = weather_icon)

kaggle_weather_Seville <- filter(kaggle_weather, city_name == "Seville") %>% 
  select(-city_name) %>% 
  rename(temp_Seville = temp, 
         temp_min_Seville = temp_min, 
         temp_max_Seville = temp_max, 
         pressure_Seville = pressure, 
         humidity_Seville = humidity, 
         wind_speed_Seville = wind_speed, 
         wind_deg_Seville = wind_deg, 
         rain_1h_Seville = rain_1h, 
         rain_3h_Seville = rain_3h, 
         snow_3h_Seville = snow_3h, 
         clouds_all_Seville = clouds_all, 
         weather_id_Seville = weather_id, 
         weather_main_Seville = weather_main, 
         weather_description_Seville = weather_description, 
         weather_icon_Seville = weather_icon)

kaggle_weather_Valencia <- filter(kaggle_weather, city_name == "Valencia") %>% 
  select(-city_name) %>% 
  rename(temp_Valencia = temp, 
         temp_min_Valencia = temp_min, 
         temp_max_Valencia = temp_max, 
         pressure_Valencia = pressure, 
         humidity_Valencia = humidity, 
         wind_speed_Valencia = wind_speed, 
         wind_deg_Valencia = wind_deg, 
         rain_1h_Valencia = rain_1h, 
         rain_3h_Valencia = rain_3h, 
         snow_3h_Valencia = snow_3h, 
         clouds_all_Valencia = clouds_all, 
         weather_id_Valencia = weather_id, 
         weather_main_Valencia = weather_main, 
         weather_description_Valencia = weather_description, 
         weather_icon_Valencia = weather_icon)

delete_duplicated_row <- function(df) {
  for (i in 1:(nrow(df)-1)) {
    if(df$dt_iso[i] == df$dt_iso[i+1]) {
      df[i, 2] <- NA
    }
  }
  drop_na(df)
}

kaggle_weather_Barcelona_35064rows <- delete_duplicated_row(kaggle_weather_Barcelona)
kaggle_weather_Bilbao_35064rows <- delete_duplicated_row(kaggle_weather_Bilbao)
kaggle_weather_Madrid_35064rows <- delete_duplicated_row(kaggle_weather_Madrid)
kaggle_weather_Seville_35064rows <- delete_duplicated_row(kaggle_weather_Seville)
kaggle_weather_Valencia_35064rows <- delete_duplicated_row(kaggle_weather_Valencia)

kaggle_weather_wider <- left_join(kaggle_weather_Barcelona_35064rows, kaggle_weather_Bilbao_35064rows, by = c("dt_iso")) %>% 
  left_join(kaggle_weather_Madrid_35064rows, by = c("dt_iso")) %>% 
  left_join(kaggle_weather_Seville_35064rows, by = c("dt_iso")) %>% 
  left_join(kaggle_weather_Valencia_35064rows, by = c("dt_iso"))

kaggle_weather_wider
```

# Combining Kaggle data into only 1 data frame

```{r}
kaggle <- left_join(kaggle_energy, kaggle_weather_wider, by = c("time" = "dt_iso"))
kaggle
```

# Checking NA

```{r}
colSums(is.na(kaggle))
```

# Filling with NA (Imputation)

```{r}
kaggle_clean <- mutate(kaggle, 
                       generation_biomass = na.approx(generation_biomass), 
                       generation_fossil_brown_coal_lignite = na.approx(generation_fossil_brown_coal_lignite),
                       generation_fossil_coal_derived_gas = na.approx(generation_fossil_coal_derived_gas),
                       generation_fossil_gas = na.approx(generation_fossil_gas), 
                       generation_fossil_hard_coal = na.approx(generation_fossil_hard_coal),
                       generation_fossil_oil = na.approx(generation_fossil_oil), 
                       generation_fossil_oil_shale = na.approx(generation_fossil_oil_shale),
                       generation_fossil_peat = na.approx(generation_fossil_peat), 
                       generation_geothermal = na.approx(generation_geothermal),
                       generation_hydro_pumped_storage_consumption = na.approx(generation_hydro_pumped_storage_consumption), 
                       generation_hydro_run_of_river_and_poundage = na.approx(generation_hydro_run_of_river_and_poundage), 
                       generation_hydro_water_reservoir = na.approx(generation_hydro_water_reservoir),
                       generation_marine = na.approx(generation_marine), 
                       generation_nuclear = na.approx(generation_nuclear), 
                       generation_other = na.approx(generation_other), 
                       generation_other_renewable = na.approx(generation_other_renewable), 
                       generation_solar = na.approx(generation_solar), 
                       generation_waste = na.approx(generation_waste), 
                       generation_wind_offshore = na.approx(generation_wind_offshore), 
                       generation_wind_onshore = na.approx(generation_wind_onshore), 
                       total_load_actual = na.approx(total_load_actual))

colSums(is.na(kaggle_clean))
```

# Adding date, hour, day, week, and year column

```{r}
kaggle_prep <- mutate(kaggle_clean, date = date(time)) %>% mutate(hour = hour(time), day = (as.POSIXlt(date)$wday + 1), week = week(time), year = year(time)) # day = 1 is Sunday and day = 7 is Saturday

kaggle_prep
```

# Adding sine and cosine of hour, day, and week column

```{r}
kaggle_prep <- mutate(kaggle_prep, 
                sin_hour = sin(2*pi*hour/24), 
                cos_hour = cos(2*pi*hour/24), 
                sin_day = sin(2*pi*day/7), 
                cos_day = cos(2*pi*day/7), 
                sin_week = sin(2*pi*week/52), 
                cos_week = cos(2*pi*week/52))

kaggle_prep
```


## Importing Renewables Ninja data

# Importing data

```{r}
ninja_weather <- read_csv('data/Renewables_Ninja/ninja_weather_country_ES_merra-2_population_weighted.csv', skip = 2)
ninja_weather
```

# Transforming time column from class character into class POSIXct/POSIXt

```{r}
ninja_weather <- mutate(ninja_weather, time = dmy_hm(time))
ninja_weather
```

# Selecting only Year 2015-2018 and adding date, hour, day, week, and year column

```{r}
ninja_weather_selected <- ninja_weather[which(ninja_weather$time == kaggle$time[1]):which(ninja_weather$time == kaggle$time[length(kaggle$time)]), ]

ninja_weather_prep <- mutate(ninja_weather_selected, date = date(time)) %>% mutate(hour = hour(time), day = (as.POSIXlt(date)$wday + 1), week = week(time), year = year(time)) # day = 1 is Sunday and day = 7 is Saturday

ninja_weather_prep
```

# Adding sine and cosine of hour, day, and week column

```{r}
ninja_weather_prep <- mutate(ninja_weather_prep, 
                             sin_hour = sin(2*pi*hour/24), 
                             cos_hour = cos(2*pi*hour/24), 
                             sin_day = sin(2*pi*day/7), 
                             cos_day = cos(2*pi*day/7), 
                             sin_week = sin(2*pi*week/52), 
                             cos_week = cos(2*pi*week/52))
                
ninja_weather_prep
```


## Dividing training and testing data

# Kaggle data

```{r}
train_kaggle <- filter(kaggle_prep, year < 2018) # train data ~ 75%
test_kaggle <- filter(kaggle_prep, year >= 2018) # test data ~ 25%

tail(train_kaggle)
head(test_kaggle)
```

# Renewables Ninja data

```{r}
train_ninja_weather <- filter(ninja_weather_prep, year < 2018) # train data ~ 75%
test_ninja_weather <- filter(ninja_weather_prep, year >= 2018) # test data ~ 25%

tail(train_ninja_weather)
head(test_ninja_weather)
```


## Solar prediction

# Checking autocorrelation of Solar generation, temperature, and irradiance

```{r}
acf(train_kaggle$generation_solar, lag.max = 48)
acf(train_ninja_weather$irradiance_surface, lag.max = 48)
acf(train_ninja_weather$irradiance_toa, lag.max = 48)
acf(train_ninja_weather$temperature, lag.max = 48)
acf(train_ninja_weather$cloud_cover, lag.max = 48)
acf(train_ninja_weather$precipitation, lag.max = 48)
acf(train_ninja_weather$snowfall, lag.max = 48)
# We want to predict tomorrow based on older than yesterday data, so the 24-hour lagged variables will be used for prediction, which are quite good representations.
```

# Selecting appropriate variables for Solar generation prediction

```{r}
prep_solar <- function(df1, df2) {
   df1 <- transmute(df1, DataTime = time, 
                   Actual_solar_gen = generation_solar, 
                   sin_hour = sin_hour, 
                   cos_hour = cos_hour, 
                   sin_week = sin_week, 
                   cos_week = cos_week,
                   lagged_24hr_solar_gen = lag(df1$generation_solar, 24))
   df2 <- transmute(df2, DataTime = time, 
                   lagged_24hr_irradiance_surface = lag(df2$irradiance_surface, 24), 
                   lagged_24hr_irradiance_toa = lag(df2$irradiance_toa, 24), 
                   lagged_24hr_temperature = lag(df2$temperature, 24), 
                   lagged_24hr_cloud_cover = lag(df2$cloud_cover, 24), 
                   lagged_24hr_precipitation = lag(df2$precipitation, 24), 
                   lagged_24hr_snowfall = lag(df2$snowfall, 24))
   df <- left_join(df1, df2, by = "DataTime")
   return(df)
}

train_solar <- prep_solar(train_kaggle, train_ninja_weather) %>% drop_na()
test_solar <- prep_solar(test_kaggle, test_ninja_weather) %>% drop_na()
train_solar
test_solar
```

# Creating with linear regression model

```{r}
solar_linear_model <- lm(Actual_solar_gen ~ .-DataTime, train_solar)
summary(solar_linear_model)
```

# Creating with decision tree model

```{r}
solar_decision_tree_model <- rpart(Actual_solar_gen ~ .-DataTime, train_solar, 
                                   minsplit = 5, minbucket = 1, cp = 0.001)
rpart.plot(solar_decision_tree_model)
```

# Comparing models

```{r}
predicted_train_solar <- transmute(train_solar, 
                              DataTime = DataTime, 
                              Actual_solar_gen = Actual_solar_gen, 
                              Predicted_linear_solar_gen = predict(solar_linear_model, train_solar), 
                              Predicted_decision_tree_solar_gen = predict(solar_decision_tree_model)) %>%
  pivot_longer(Predicted_linear_solar_gen:Predicted_decision_tree_solar_gen, names_to = "model", values_to = "predicted") %>% 
  mutate(residual = predicted - Actual_solar_gen)

predicted_train_solar
```

# Model evaluation

```{r}
r_squared <- function(actual, predicted) {
  ans <- 1- (sum((actual - predicted)^2)/sum((actual - mean(actual))^2))
  return(ans)
}

mape <- function(actual, predicted, train) {
  ans <- mean(if_else(actual != 0, abs(actual - predicted)/actual, 0))*100
  return(ans)
}
```

```{r}
Acc_metrics <- group_by(predicted_train_solar, model) %>% 
  summarise(R_squared = r_squared(Actual_solar_gen, predicted), 
            MAPE = mape(Actual_solar_gen, predicted, train_solar),
            MAE = mae(Actual_solar_gen, predicted))

Acc_metrics
```

## Onshore Wind prediction

# Checking autocorrelation of Onshore wind generation, pressure, wind speed, and wind direction

```{r}
acf(train_kaggle$generation_wind_onshore, lag.max = 48)
acf(train_kaggle$wind_speed_Barcelona, lag.max = 48)
acf(train_kaggle$wind_deg_Barcelona, lag.max = 48)
acf(train_kaggle$wind_speed_Bilbao, lag.max = 48)
acf(train_kaggle$wind_deg_Bilbao, lag.max = 48)
acf(train_kaggle$wind_speed_Madrid, lag.max = 48)
acf(train_kaggle$wind_deg_Madrid, lag.max = 48)
acf(train_kaggle$wind_speed_Seville, lag.max = 48)
acf(train_kaggle$wind_deg_Seville, lag.max = 48)
acf(train_kaggle$wind_speed_Valencia, lag.max = 48)
acf(train_kaggle$wind_deg_Valencia, lag.max = 48)
acf(train_kaggle$pressure_Barcelona, lag.max = 48)
acf(train_kaggle$pressure_Bilbao, lag.max = 48)
acf(train_kaggle$pressure_Madrid, lag.max = 48)
acf(train_kaggle$pressure_Seville, lag.max = 48)
acf(train_kaggle$pressure_Valencia, lag.max = 48)
# We want to predict tomorrow based on older than yesterday data, so the 24-hour lagged variables will be used for prediction. However, they are not that good representations, but ACFs are still around 0.5, which is quite acceptable.
```

# Selecting appropriate variables for Onshore Wind generation prediction

```{r}
prep_wind <- function(df) {
   df <- transmute(df, DataTime = time, 
                   Actual_onshore_wind_gen = generation_wind_onshore, 
                   sin_hour = sin_hour, 
                   cos_hour = cos_hour, 
                   sin_week = sin_week, 
                   cos_week = cos_week,
                   lagged_24hr_onshore_wind_gen = lag(df$generation_wind_onshore, 24),
                   lagged_24hr_wind_speed_Barcelona = lag(df$wind_speed_Barcelona, 24),
                   lagged_24hr_wind_deg_Barcelona = lag(df$wind_deg_Barcelona, 24),
                   lagged_24hr_wind_speed_Bilbao = lag(df$wind_speed_Bilbao, 24),
                   lagged_24hr_wind_deg_Bilbao = lag(df$wind_deg_Bilbao, 24),
                   lagged_24hr_wind_speed_Madrid = lag(df$wind_speed_Madrid, 24),
                   lagged_24hr_wind_deg_Madrid = lag(df$wind_deg_Madrid, 24),
                   lagged_24hr_wind_speed_Seville = lag(df$wind_speed_Seville, 24),
                   lagged_24hr_wind_deg_Seville = lag(df$wind_deg_Seville, 24),
                   lagged_24hr_wind_speed_Valencia = lag(df$wind_speed_Valencia, 24),
                   lagged_24hr_wind_deg_Valencia = lag(df$wind_deg_Valencia, 24),
                   lagged_24hr_pressure_Barcelona = lag(df$pressure_Barcelona, 24), 
                   lagged_24hr_pressure_Bilbao = lag(df$pressure_Bilbao, 24),
                   lagged_24hr_pressure_Madrid = lag(df$pressure_Madrid, 24),
                   lagged_24hr_pressure_Seville = lag(df$pressure_Seville, 24),
                   lagged_24hr_pressure_Valencia = lag(df$pressure_Valencia, 24))
   return(df)
}

train_wind <- prep_wind(train_kaggle) %>% drop_na()
test_wind <- prep_wind(test_kaggle) %>% drop_na()
train_wind
test_wind
```

# ////////////Creating with linear regression model

```{r}
wind_linear_model <- lm(Actual_onshore_wind_generation ~ .-DataTime, train_wind)

predicted_train_wind <- transmute(train_wind, 
                              DataTime = DataTime, 
                              Actual_onshore_wind_generation = Actual_onshore_wind_generation, 
                              Predicted_linear_onshore_wind_generation = predict(wind_linear_model, train_wind))

predicted_train_wind
```


## Demand prediction

# ////////////Assuming that this week demand equals to next week demand (Naive prediction)

```{r}
predicted_demand <- transmute(kaggle, DataTime = time, Actual_demand = kaggle$'total load actual', Predicted_demand = lag(kaggle$'total load actual', 24*7)) %>% drop_na()
predicted_demand
```


## Evaluating model performance

# ////////////Evaluating model performance of Solar prediction

```{r}
rmse(predicted_train_solar$Actual_solar_generation, predicted_train_solar$Predicted_linear_solar_generation)
```

# ////////////Evaluating model performance of Onshore Wind prediction

```{r}
rmse(predicted_train_wind$Actual_onshore_wind_generation, predicted_train_wind$Predicted_linear_onshore_wind_generation)
```

# ////////////Evaluating model performance of Demand prediction

```{r}
rmse(predicted_demand$Actual_demand, predicted_demand$Predicted_demand)
```

