---
title: "Test"
output: html_document
---

## Loading packages

```{r}
library(tidyverse)
library(lubridate)
library(zoo)
library(boot)
library(rpart)
library(rpart.plot)
library(modelr)
library(randomForest)
```


## Importing Kaggle data

# Importing Kaggle's Energy generation, demand, and prices data

```{r}
kaggle_energy <- read_csv('data/Energy_demand_Generation_and_Prices_Spain/energy_dataset.csv')

names(kaggle_energy) <- gsub(" ", "_", names(kaggle_energy))
names(kaggle_energy) <- gsub("/", "_", names(kaggle_energy))
names(kaggle_energy) <- gsub("-", "_", names(kaggle_energy))

kaggle_energy
```

# Creating Non-renewable generation's data frame, Renewable generation's data frame, Solar generation's data frame, Onshore wind generation's data frame, and Total generation data frame

```{r}
kaggle_energy_non_renewable <- select(kaggle_energy, time, generation_fossil_brown_coal_lignite, generation_fossil_gas, generation_fossil_hard_coal, generation_fossil_oil, generation_nuclear, generation_other)

kaggle_energy_renewable <- select(kaggle_energy, time, generation_biomass, generation_hydro_pumped_storage_consumption, generation_hydro_run_of_river_and_poundage, generation_hydro_water_reservoir, generation_waste, generation_solar, generation_wind_onshore, generation_other_renewable)

kaggle_energy_solar <- select(kaggle_energy, time, generation_solar)

kaggle_energy_onshore_wind <- select(kaggle_energy, time, generation_wind_onshore)

kaggle_energy_total_gen <- left_join(kaggle_energy_non_renewable, kaggle_energy_renewable, by = "time")
kaggle_energy_total_gen <- transmute(kaggle_energy_total_gen, time = time, total_generation = rowSums(select(kaggle_energy_total_gen, -time)))

kaggle_energy_solar
kaggle_energy_onshore_wind
kaggle_energy_total_gen
```

# Importing Kaggle's Weather data

```{r}
kaggle_weather <- read_csv('data/Energy_demand_Generation_and_Prices_Spain/weather_features.csv')
kaggle_weather
```

# Pre-processing Kaggle's Weather data: CASE 1 adding variables (columns) of all cities

```{r}
# kaggle_weather_wider <- read_csv('data/Energy_demand_Generation_and_Prices_Spain/kaggle_weather_wider.csv')

kaggle_weather_Barcelona <- filter(kaggle_weather, city_name == "Barcelona") %>% 
  select(-city_name) %>% 
  rename(temp_Barcelona = temp, 
         temp_min_Barcelona = temp_min, 
         temp_max_Barcelona = temp_max, 
         pressure_Barcelona = pressure, 
         humidity_Barcelona = humidity, 
         wind_speed_Barcelona = wind_speed, 
         wind_deg_Barcelona = wind_deg, 
         rain_1h_Barcelona = rain_1h, 
         rain_3h_Barcelona = rain_3h, 
         snow_3h_Barcelona = snow_3h, 
         clouds_all_Barcelona = clouds_all, 
         weather_id_Barcelona = weather_id, 
         weather_main_Barcelona = weather_main, 
         weather_description_Barcelona = weather_description, 
         weather_icon_Barcelona = weather_icon)

kaggle_weather_Bilbao <- filter(kaggle_weather, city_name == "Bilbao") %>% 
  select(-city_name) %>% 
  rename(temp_Bilbao = temp, 
         temp_min_Bilbao = temp_min, 
         temp_max_Bilbao = temp_max, 
         pressure_Bilbao = pressure, 
         humidity_Bilbao = humidity, 
         wind_speed_Bilbao = wind_speed, 
         wind_deg_Bilbao = wind_deg, 
         rain_1h_Bilbao = rain_1h, 
         rain_3h_Bilbao = rain_3h, 
         snow_3h_Bilbao = snow_3h, 
         clouds_all_Bilbao = clouds_all, 
         weather_id_Bilbao = weather_id, 
         weather_main_Bilbao = weather_main, 
         weather_description_Bilbao = weather_description, 
         weather_icon_Bilbao = weather_icon)

kaggle_weather_Madrid <- filter(kaggle_weather, city_name == "Madrid") %>% 
  select(-city_name) %>% 
  rename(temp_Madrid = temp, 
         temp_min_Madrid = temp_min, 
         temp_max_Madrid = temp_max, 
         pressure_Madrid = pressure, 
         humidity_Madrid = humidity, 
         wind_speed_Madrid = wind_speed, 
         wind_deg_Madrid = wind_deg, 
         rain_1h_Madrid = rain_1h, 
         rain_3h_Madrid = rain_3h, 
         snow_3h_Madrid = snow_3h, 
         clouds_all_Madrid = clouds_all, 
         weather_id_Madrid = weather_id, 
         weather_main_Madrid = weather_main, 
         weather_description_Madrid = weather_description, 
         weather_icon_Madrid = weather_icon)

kaggle_weather_Seville <- filter(kaggle_weather, city_name == "Seville") %>% 
  select(-city_name) %>% 
  rename(temp_Seville = temp, 
         temp_min_Seville = temp_min, 
         temp_max_Seville = temp_max, 
         pressure_Seville = pressure, 
         humidity_Seville = humidity, 
         wind_speed_Seville = wind_speed, 
         wind_deg_Seville = wind_deg, 
         rain_1h_Seville = rain_1h, 
         rain_3h_Seville = rain_3h, 
         snow_3h_Seville = snow_3h, 
         clouds_all_Seville = clouds_all, 
         weather_id_Seville = weather_id, 
         weather_main_Seville = weather_main, 
         weather_description_Seville = weather_description, 
         weather_icon_Seville = weather_icon)

kaggle_weather_Valencia <- filter(kaggle_weather, city_name == "Valencia") %>% 
  select(-city_name) %>% 
  rename(temp_Valencia = temp, 
         temp_min_Valencia = temp_min, 
         temp_max_Valencia = temp_max, 
         pressure_Valencia = pressure, 
         humidity_Valencia = humidity, 
         wind_speed_Valencia = wind_speed, 
         wind_deg_Valencia = wind_deg, 
         rain_1h_Valencia = rain_1h, 
         rain_3h_Valencia = rain_3h, 
         snow_3h_Valencia = snow_3h, 
         clouds_all_Valencia = clouds_all, 
         weather_id_Valencia = weather_id, 
         weather_main_Valencia = weather_main, 
         weather_description_Valencia = weather_description, 
         weather_icon_Valencia = weather_icon)

delete_duplicated_row <- function(df) {
  for (i in 1:(nrow(df)-1)) {
    if(df$dt_iso[i] == df$dt_iso[i+1]) {
      df[i, 2] <- NA
    }
  }
  drop_na(df)
}

kaggle_weather_Barcelona_35064rows <- delete_duplicated_row(kaggle_weather_Barcelona)
kaggle_weather_Bilbao_35064rows <- delete_duplicated_row(kaggle_weather_Bilbao)
kaggle_weather_Madrid_35064rows <- delete_duplicated_row(kaggle_weather_Madrid)
kaggle_weather_Seville_35064rows <- delete_duplicated_row(kaggle_weather_Seville)
kaggle_weather_Valencia_35064rows <- delete_duplicated_row(kaggle_weather_Valencia)

kaggle_weather_wider <- left_join(kaggle_weather_Barcelona_35064rows, kaggle_weather_Bilbao_35064rows, by = c("dt_iso")) %>% 
  left_join(kaggle_weather_Madrid_35064rows, by = c("dt_iso")) %>% 
  left_join(kaggle_weather_Seville_35064rows, by = c("dt_iso")) %>% 
  left_join(kaggle_weather_Valencia_35064rows, by = c("dt_iso"))

kaggle_weather_wider

# write.csv(kaggle_weather_wider,"data/Energy_demand_Generation_and_Prices_Spain/kaggle_weather_wider.csv")
```

# Pre-processing Kaggle's Weather data: CASE 2 taking mean variables of all cities

```{r}
kaggle_weather_mean <- group_by(kaggle_weather, dt_iso) %>% 
  summarise(temp = mean(temp), temp_min = mean(temp_min), temp_max = mean(temp_max), pressure = mean(pressure), 
            humidity = mean(humidity), wind_speed = mean(wind_speed), wind_deg = mean(wind_deg), 
            rain_1h = mean(rain_1h), rain_3h = mean(rain_3h), snow_3h = mean(snow_3h), clouds_all = mean(clouds_all)) %>% rename(time = dt_iso)

kaggle_weather_mean
```

# Combining Kaggle data into only 1 data frame to check whether there is any NA

```{r}
kaggle <- left_join(kaggle_energy_solar, kaggle_energy_onshore_wind, by = "time") %>%
  left_join(kaggle_energy_total_gen, by = "time") %>% 
  left_join(kaggle_weather_mean, by = "time")

colSums(is.na(kaggle))
```

# Filling with NA (Imputation) using linear interpolation method

```{r}
kaggle_energy_solar <- mutate(kaggle_energy_solar,
                              generation_solar = na.approx(generation_solar))

kaggle_energy_onshore_wind <- mutate(kaggle_energy_onshore_wind,
                                     generation_wind_onshore = na.approx(generation_wind_onshore))

kaggle_energy_total_gen <- mutate(kaggle_energy_total_gen,
                                  total_generation = na.approx(total_generation))

kaggle_energy_solar_and_wind <- left_join(kaggle_energy_solar, kaggle_energy_onshore_wind, by = "time")
kaggle_energy_solar_and_wind <- transmute(kaggle_energy_solar_and_wind, time = time, solar_and_wind_generation = rowSums(select(kaggle_energy_solar_and_wind, -time)))

kaggle_energy <- left_join(kaggle_energy_solar_and_wind, kaggle_energy_total_gen, by = "time") %>% 
  mutate(percent_solar_and_wind_penetration = 100*solar_and_wind_generation/total_generation)
kaggle_energy
```


## Importing Renewables Ninja data

# Importing data

```{r}
ninja_weather <- read_csv('data/Renewables_Ninja/ninja_weather_country_ES_merra-2_population_weighted.csv', skip = 2)
ninja_weather
```

# Transforming time column from class character into class POSIXct/POSIXt and Selecting only Year 2015-2018

```{r}
ninja_weather <- mutate(ninja_weather, time = dmy_hm(time))

ninja_weather_selected <- ninja_weather[which(ninja_weather$time == kaggle$time[1]):which(ninja_weather$time == kaggle$time[length(kaggle$time)]), ]

ninja_weather_selected
```

# Adding hour, day, and week column and Adding sine and cosine of hour, day, and week column

```{r}
ninja_weather_prep <- mutate(ninja_weather_selected, 
                             hour = hour(time), 
                             day = (as.POSIXlt(date(time))$wday + 1), # day = 1 is Sunday and day = 7 is Saturday
                             week = week(time)) %>% 
  mutate(sin_hour = sin(2*pi*hour/24),
         cos_hour = cos(2*pi*hour/24),
         sin_day = sin(2*pi*day/7), 
         cos_day = cos(2*pi*day/7),
         sin_week = sin(2*pi*week/52), 
         cos_week = cos(2*pi*week/52)) %>% 
  select(-hour, -day, -week)

ninja_weather_prep
```


## Dividing training and testing data

# Creating function to split training and test data

```{r}
train_test_splitting <- function(df, string) {
  if (string == "training") {
    df <- filter(df, year(df$time) < 2018)
    return(df)
  }
  else if (string == "test") {
    df <- filter(df, year(df$time) >= 2018)
    return(df)
  }
  else {print("Something wrong!")}
}
```

# Kaggle energy data

```{r}
train_kaggle_energy <- train_test_splitting(kaggle_energy, "training") # train data ~ 75%
test_kaggle_energy <- train_test_splitting(kaggle_energy, "test") # test data ~ 25%

tail(train_kaggle_energy)
head(test_kaggle_energy)
```

# Kaggle Weather data

```{r}
train_kaggle_weather <- train_test_splitting(kaggle_weather_mean, "training") # train data ~ 75%
test_kaggle_weather <- train_test_splitting(kaggle_weather_mean, "test") # test data ~ 25%

tail(train_kaggle_weather)
head(test_kaggle_weather)
```

# Renewables Ninja Weather data

```{r}
train_ninja_weather <- train_test_splitting(ninja_weather_prep, "training") # train data ~ 75%
test_ninja_weather <- train_test_splitting(ninja_weather_prep, "test") # test data ~ 25%

tail(train_ninja_weather)
head(test_ninja_weather)
```


## Solar and Onshore Wind prediction

# Selecting features (independent variables) to fit model : preparing the data frame

```{r}
train_solar_and_wind_prep <- transmute(train_kaggle_energy, time,
                                       Actual_solar_and_wind_gen = solar_and_wind_generation,
                                       lagged_24hr_solar_and_wind_gen = lag(solar_and_wind_generation, 24)) %>%
  left_join(train_kaggle_weather, by = "time") %>% 
  left_join(train_ninja_weather, by = "time") %>% drop_na()
  
train_solar_and_wind_prep
```

# Selecting features (independent variables) to fit model : Checking correlation coefficient of each variables

```{r}
Cor_coefficient_to_solar_and_wind_gen <- matrix(data = 0, nrow = ncol(train_solar_and_wind_prep) - 2, ncol = 1,
                                                dimname = list(names(train_solar_and_wind_prep)[-c(1, 2)],
                                                               "Correlation_coefficient_to_solar_and_wind_gen"))

for(i in 1:nrow(Cor_coefficient_to_solar_and_wind_gen)) {
  Cor_coefficient_to_solar_and_wind_gen[i, 1] <- cor(train_solar_and_wind_prep[, 2], train_solar_and_wind_prep[, i+2])
}

Cor_coefficient_to_solar_and_wind_gen[order(abs(Cor_coefficient_to_solar_and_wind_gen), decreasing = TRUE), ]
```

# Selecting appropriate features for Solar generation prediction

```{r}
train_solar_and_wind <- select(train_solar_and_wind_prep, time, 
                               Actual_solar_and_wind_gen,
                               lagged_24hr_solar_and_wind_gen, 
                               sin_hour,
                               cos_hour,
                               sin_week,
                               cos_week,
                               wind_speed,
                               irradiance_surface,
                               humidity,
                               temperature,
                               rain_1h,
                               cloud_cover,
                               pressure)
train_solar_and_wind
```

# Doing 1st order linear regression model

```{r}
solar_and_wind_linear_model_1st_order <- lm(Actual_solar_and_wind_gen ~ .-time, train_solar_and_wind)
summary(solar_and_wind_linear_model_1st_order)
```

# Doing 3rd order linear regression model

```{r}
solar_and_wind_linear_model_3rd_order <- lm(Actual_solar_and_wind_gen ~ (.-time)^3, train_solar_and_wind)
summary(solar_and_wind_linear_model_3rd_order)
```

# Creating with decision tree model

```{r}
solar_and_wind_decision_tree_model <- rpart(Actual_solar_and_wind_gen ~ .-time, train_solar_and_wind,
                                            minsplit = 5, minbucket = 1, cp = 0.001)
rpart.plot(solar_and_wind_decision_tree_model)
```

# Creating with random forest model

```{r}
solar_and_wind_random_forest_model <- randomForest(Actual_solar_and_wind_gen ~ .-time, train_solar_and_wind, 
                                                   ntree = 20)
```

```{r}
predicted_train_solar_and_wind <- transmute(train_solar_and_wind, time = time,
                                   actual = Actual_solar_and_wind_gen,
                                   Predicted_Naive_solar_gen = lagged_24hr_solar_and_wind_gen,
                                   Predicted_1st_linear_solar_and_wind_gen = predict(solar_and_wind_linear_model_1st_order,train_solar_and_wind),
                                   Predicted_3rd_linear_solar_and_wind_gen = predict(solar_and_wind_linear_model_3rd_order,train_solar_and_wind), 
                                   Predicted_decision_tree_solar_and_wind_gen = predict(solar_and_wind_decision_tree_model,train_solar_and_wind),
                                   Predicted_random_forest_solar_and_wind_gen = predict(solar_and_wind_random_forest_model,train_solar_and_wind)) %>%
  pivot_longer(Predicted_Naive_solar_gen:Predicted_random_forest_solar_and_wind_gen, names_to = "model", values_to = "predicted") %>% 
  mutate(residual = predicted - actual)

predicted_train_solar_and_wind
```

# Model evaluation

```{r}
r_squared <- function(actual, predicted) {
  ans <- 1- (sum((actual - predicted)^2)/sum((actual - mean(actual))^2))
  return(ans)
}

rmse <- function(actual, predicted) {
  answer <- sqrt(mean((actual - predicted)^2))
  return(answer)
}

mape <- function(actual, predicted) {
  ans <- mean(if_else(actual != 0, abs(actual - predicted)/actual, 0))*100
  return(ans)
}
```

```{r}
Acc_metrics <- group_by(predicted_train_solar_and_wind, model) %>% 
  summarise(R_squared = r_squared(actual, predicted),
            RMSE = rmse(actual, predicted), 
            MAPE = mape(actual, predicted))

Acc_metrics
```

